---
title: "Quick demo"
output: 
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    fig_caption: yes
    toc: false
    number_sections: false
pkgdown:
  as_is: true
bibliography: refs.bib
csl: apa-old-doi-prefix.csl
vignette: >
  %\VignetteIndexEntry{Quick demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", echo = TRUE, message = FALSE, warning = FALSE
)
```

```{r setup}
# remotes::install_github("PengSU517/regcell")
library(regcell)
library(tidyverse)
```


## A simulated dataset

We generate a dataset that incorporates a design matrix with 200 observations and 50 variables. The contamination rate is set to 5%, and the scale of residuals is fixed at 3, while retaining the default values for other settings.

```{r}

set.seed(1234)
dat = regcell::genevar(n = 200, p = 50, e = 0.05, sigma = 3) 

y = dat$y
x = dat$x
```

## Outlier detection

Detect outliers using DDC [@rousseeuw_detecting_2018].

```{r fig.height=3.5, fig.width=10}

fit1 <- cellWise::DDC(x)
p1 = regcell::newcellmap(fit1$stdResid, columnlabels = c(dim(x)[2],rep(" ",dim(x)[2]-2),1), rowlabels = c(dim(x)[1],rep(" ",dim(x)[1]-2),1), columnangle = 0,
        rowtitle = "Observations", columntitle = "Variables", sizetitles = 2,adjustrowlabels = 0.5, adjustcolumnlabels = 0.5)+
   theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        legend.title = element_text(size=14), #change legend title font size
        legend.text = element_text(size=12)) +
  coord_flip()
p1
```

## Model training

We establish a training set and a testing set. Subsequently, we employ the training set to fit models and assess prediction errors by evaluating their performance on the testing set.

```{r}
set.seed(1234)
inTrain <- caret::createDataPartition(y, p = 0.7)[[1]]


ytrain = y[inTrain]
xtrain = x[inTrain,]

ytest = y[-inTrain]
xtest = x[-inTrain,]
```

```{r}
set.seed(1234)
#fit a model using CR-Lasso
fit0 = sregcell_std(ytrain,xtrain)
res = ytest - fit0$intercept_hat - xtest%*%fit0$betahat

#fit a model using RLars
fit1 = Rlars(ytrain,xtrain)
res2 = ytest - fit1$betahat[1] - xtest%*%fit1$betahat[-1]
```

The figure below illustrates the distribution of prediction errors derived from the test set.

```{r fig.height=7, fig.width=7}
df = data.frame(res = c(res, res2), 
                method = c(rep("CR-Lasso", length(res)),rep("RLars", length(res)) ))
boxplot(res~method, outline = FALSE, data = df)
```












