---
title: "realdata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{realdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE
)
```

```{r setup}
library(regcell)
library(tidyverse)
```

# Load raw datasets

Load the original datasets and retain the necessary variables.

Raw datasets are from https://www.ebi.ac.uk/arrayexpress/experiments/E-MEXP-1618/.

```{r}
###load the micro-array dataset
dat = as.data.frame(t(read.csv("Normarrayexpressdata.txt.magetab", sep = "\t")))
datc = dat
colnames(datc) = datc[1,]
datcc = datc[-1,]

colnames(datcc)[1] = "id"
datcc$id = extract_numeric(rownames(datcc))

### load the feature dataset
featuredat = read.csv("E-MEXP-1618.sdrf.txt", sep = "\t")
featuredat$id = extract_numeric(featuredat$Source.Name)

# merge them and keep necessary variables
datall = merge(featuredat, datcc, by = "id")
y = datall$Characteristics..Total.Hip.T.score.
x = datall[,-(1:50)] %>% mutate(across(.fns = as.numeric))
logx = log(x)

data_bmd = cbind(y, logx)
save(data_bmd, file = "data_bmd.RData")
```


# Screen variables

Screen correlated variables according to a robust correlation estimate based on Winsorization.
The screened dataset `datascreen` is included in this package.

```{r}
x = data_bmd[,-1]
y = data_bmd[,1]

xnormal = x

## calculate robust correlation and screen variables
corh = apply(xnormal,2, function(xvec){robustHD::corHuber(xvec,y)})   ## huber correlation
orders = order(abs(corh), decreasing = T)
xscreen = (xnormal[,orders])[,1:100]
# corh_screened = apply(xscreen,2, function(xvec){robustHD::corHuber(xvec,y)})
# pairs(cbind(y,xscreen[,1:5]))

datascreen = cbind(y,xscreen)
save(datascreen, file = "datascreen.RData")


```


# All methods compared

```{r}
##### methods compared
mtds = list(
  ## spase shooting S, codes arefrom https://github.com/ineswilms/sparse-shooting-S 
  ## package is available from https://github.com/PengSU517/shootings
  # sss = function(y, x){shootings::sparseshooting(x,y)$coef},
  
  ## Rlars, from package robustHD
  rlars = function(y, x){regcell::Rlars(y, x)$betahat}, 
  
  ## MM-Lasso, from https://github.com/esmucler/mmlasso
  # mmlasso = function(y,x){mmlasso::mmlasso(x,y)$coef.MMLasso.ad}, 
  
  ## sparse LTS, from package robustHD
  slts = function(y,x){regcell::SLTS(y,x)$betahat},
  
  ## cellwise regularized Lasso without post regression
  cell_lasso = function(y,x){ 
    fit = regcell::sregcell_std(y = y, x = x, softbeta = TRUE, lambda_zeta = 1, penal = 1, penaldelta =0)
    return(c(fit$intercept_hat, fit$betahat))
  },

  ## cellwise regularized Lasso with post regression
  cell_lasso_post = function(y,x){
    fit = regcell::sregcell_std(y = y, x = x, softbeta = TRUE, lambda_zeta = 1, penal = 1, penaldelta =0)
    return(c(fit$intercept_hat_post, fit$betahat_post))
  },

  ## Lasso, from package glmnet
  lasso  = function(y,x){ 
    return(regcell::lassocv(y,x)$betahat)
  }

)
```


# Analysis with artifically generated response

```{r}
library(doParallel)
registerDoParallel(cores=10)
getDoParWorkers()

data(datascreen)
x = as.matrix(robustHD::robStandardize(datascreen[,-1])[,1:100])
ximp = cellWise::DDC(x)$Ximp

result <- foreach(mtd = 1:length(mtds),
                  .packages = c("robustHD", "robustbase" , "mmlasso", "shootings", "cellWise", "regcell"))%:%
  foreach(pr = c(5,10))%:%
  foreach(sigma = c(0.5, 1))%:%
  foreach(m = 1:200)%dopar%{
    set.seed(m)
    error = rnorm(84, sd = sigma)
    beta = sample(c(runif(pr, 1, 1.5),rep(0,100-pr)))

    y = ximp%*%beta + error
    obs = sample(1:84, 17, replace = FALSE)

    ytrain = y[-obs]
    xtrain = x[-obs,]
    ytest = y[obs]
    xtest = ximp[obs,]

    betahat = mtds[[mtd]](ytrain,xtrain)

    tpf<-function(betahat, beta){sum((as.logical(betahat)==as.logical(beta))[which(beta!=0)])}
    tnf<-function(betahat,beta){sum((as.logical(betahat)==as.logical(beta))[which(beta==0)])}
    tp = tpf(betahat[-1], beta)
    tn = tnf(betahat[-1], beta)

    res = ytest - betahat[1] - xtest%*%betahat[-1]
    mape = mean(abs(res))
    rmspe = sqrt(mean(res^2))
    rst = c(m = m, mtd = names(mtds)[mtd], pr = pr, sigma = sigma,
            tp = tp, tn = tn, rmspe = rmspe, mape = mape)

    rst
  }


save(result, file = "result_realdata_artificial.RData")

```


# Leave-one-out Cross-Validation


```{r}

data(datascreen)

y = datascreen[,1]
x = as.matrix(robustHD::robStandardize(datascreen[,-1]))
result <- foreach(mtd = 1:length(mtds),
                  .packages = c("robustHD", "robustbase" , "mmlasso","shootings", "cellWise", "regcell"))%:%
  foreach(p = c(100))%:%
  foreach(obs = 1:84)%dopar%{

    set.seed(1)
    x = x[,1:p]
    ytrain = y[-obs]
    xtrain = as.matrix(x[-obs,])
    ytest = y[obs]
    xtest = x[obs,]

    betahat = mtds[[mtd]](ytrain,xtrain)

    res = ytest - betahat[1] - sum(xtest*betahat[-1])
    rst = c(mtd = names(mtds)[mtd], n = obs, p = p, res = res)

    rst
  }


save(result, file = "result_realdata.RData")
```

